The Name of the Title is Hope

### 2020-03-19 future.tex

F U T U R E

>>>>

\subsection{Methodology changes}
After encountering only one participant with minimal Haskell knowledge it became
clear we needed to randomize the treatment for each task.
%
This would mitigate the effects of outliers on any one variant, distributing
their effect on each treatment.
%

\subsection{Future Directions}
This work touches on but does not seek to evaluate whether recognition of a
correct solution or recall of necessary parts of a correct solution are more
useful in this type-directed search setting.
%
In our \noexamples group, participants largely relied on the interpreter to tell
them what different parts of a candidate solution were doing.
%
In effect, they used the interpreter as a source of documentation.
%
So, it remains to be seen what kinds of tasks users accomplish faster with
documentation as an aid vs input-output examples.
%
